The Puzzle of the Distinct Solitude Experiences in Our Daily Life

### 2022-04-27 outputs/paper/paper.Rmd
final ver

I fit two models using all of the selected variables, one for the positive solitude affect and the other one for the negative solitude affect. The variables are age, gender, the rate of overall well being, social network size, social relationship quality, social self-efficacy, the self-reflection, solitude time, and anxiety level.\
From the below table(Table \@ref(tab:vif), we can see that all of the VIF values are relatively small. So, we decided to keep all those variables in the full models. Then, I use the backward selection to help me select the best model. Our full model for positive solitude affect contains nine variables: age, gender, the rate of overall well-being, social network size, social relationship quality, social self-efficacy, self-reflection, solitude time, and anxiety level. The backward selection model removes six variables from my full model. Thus, the backward selection model for the positive solitude experiences has only three variables; age, social quality, and self-efficacy. And those variables are concluded as having the most correlation with the positive solitude experiences. Our full model for the negative solitude affect contains nine variables as well. The backward selection model also removes six variables from my full model. Thus, the backward selection model for the negative solitude affect has three variables; age, social quality, and anxiety level. And those variables are concluded as having the most correlation with the negative solitude affect.\

@@

Let's also look at the model for the negative solitude affect. The following table includes the estimated results for this model(Table \@ref(tab:negt).

@@

## Data Sheet

>>>>

I fit two models using all of the selected variables, one for the positive solitude affect and the other one for the negative solitude affect. The variables are age, gender, the rate of overall well being, social network size, social relationship quality, social self-efficacy, the self-reflection, solitude time, and anxiety level.\
From the below table(Table \@ref(tab:vif), we can see that all of the VIF values are relatively small(Note: the vif values for both models are the same because the predictors in both models are the same). So, we decided to keep all those variables in the full models. Then, I use the backward selection to help me select the best model. Our full model for positive solitude affect contains nine variables: age, gender, the rate of overall well-being, social network size, social relationship quality, social self-efficacy, self-reflection, solitude time, and anxiety level. The backward selection model removes six variables from my full model. Thus, the backward selection model for the positive solitude experiences has only three variables; age, social quality, and self-efficacy. And those variables are concluded as having the most correlation with the positive solitude experiences. Our full model for the negative solitude affect contains nine variables as well. The backward selection model also removes six variables from my full model. Thus, the backward selection model for the negative solitude affect has three variables; age, social quality, and anxiety level. And those variables are concluded as having the most correlation with the negative solitude affect.\

@@

Let's also look at the model for the negative solitude affect. The following table includes the estimated results for this model(Table \@ref(tab:negt)).

@@

**Data Sheet**:
\
